### 2016-09-30 comparison_with_mma.tex
I disagree that ** for exponentiation is "unlike the usual programming convention"
Several languages use this, not just Python. It's also quite common even for
languages that don't have an exponentiation operator for ^ to mean xor, not
exponentiation.

SymPy, in accordance with Python (and unlike the usual programming convention),
uses \texttt{**} to express the power operator, while Mathematica uses the more
common \verb|^|.

>>>>

SymPy, in accordance with Python,
uses \texttt{**} to express the power operator, while Mathematica uses the more
common \verb|^|.
